Weather Data Integration and Assimilation System\\

### 2020-02-13 Paper.tex
Fixed: “Section”
- Add “Section”
- “section” -> “Section”

\subsection{Discussion}
\paragraph{Latency}
The latency for each operation type kept constant over the whole test plan run time without any significant change. When the request size increased from 24 data points to 96 data points, the latency increase throw out the whole test plan with a smaller number. But for each test run the latency kept constant over the time.
During the \ref{subse:obs_test_plan_all_auto_15min} test run, the performance of the Grid data got better when compared to the \ref{subse:obs_test_plan_all_15min}. Which means by adding more resources to the \acrshort{wdias}, it can handle more workload on the system.

@@

\paragraph{Resource Utilization}
Since \acrshort{wdias} using the \acrshort{k8s} as the container orchestration system, it allows to scale up and cool down the system as required based on the workload. This demonstrate on the test plan of \ref{subse:obs_test_plan_all_auto_15min}, and the system get scale up to the maximum at the peak time. Then cool down to single pod after finishing the test cases.
Given above \acrshort{wdias} can run from 1 CPU node to nodes with 100 CPUs. As described in the \ref{se:microservice}, it uses the many of the concept of modern microservice architecture to create stateless, failover, redundant microservice to achieve such capabilities.

@@

\paragraph{Grid data performance}
As mentioned in the \ref{se:conclusion}, the adapter-grid is using a Python wrapper for netCDF FORTRAN implementation with parallel IO enabled. This has some performance issues as well as memory leak issues. Since each microservice in the \acrshort{wdias} independent of technology that can use to implement the service, it will increase the performance if the adapter-grid directly ported to netCDF with a low level language such as C or FORTRAN. They are some future work that can focus on improving the performance of grid data.

@@

\paragraph{Further improve hierarchical database performance}
As further described in \ref{se:conclusion}, it is possible to increase the performance of these bottlenecks much higher such as using \acrshort{influxdb} Commercial cluster support for high availability or horizontal scaling of \acrshort{influxdb}. With \acrshort{influxdb} cluster, it is possible to run multiple pods of adapter-scalar and adapter-vector for support more server hits per second.
Other than that, the \acrshort{wdias} performance can improve via partitioning the timeseries key space into multiple \acrshort{influxdb} instances. The adapter-scalar or adapter-vector can improve to plug multiple instance of \acrshort{influxdb} instances by changing the configurations. As an example, based on the key attribute \ref{subse:timeseries_key_attributes} Timeseries Type, the adapter-scalar can connect to four instance of \acrshort{influxdb} instances such as  External Historical, External Forecast, Simulated Historical, and Simulated Forecast etc.

@@

\acrshort{wdias} performance test is perform using the \acrshort{jmeter} tool's distributed testing capabilities which separately testing each modules. Then the test plans are performed with increasing the request size, and monitored the performance metrics. The system is setup on the \acrfull{eks} as per the configurations of \ref{subse:test_sys_config}.
During the performance test plans, the system were able to provide constant throughput by keeping the latency constant while increasing the workload. Which exhibit the scalability of the system.
With the \acrshort{k8s} auto scaling, the \acrshort{wdias} were able to elastically adjust the number of pods according to the workload with the given configurations.

>>>>

\subsection{Discussion}
\paragraph{Latency}
The latency for each operation type kept constant over the whole test plan run time without any significant change. When the request size increased from 24 data points to 96 data points, the latency increase throw out the whole test plan with a smaller number. But for each test run the latency kept constant over the time.
During the Section \ref{subse:obs_test_plan_all_auto_15min} test run, the performance of the Grid data got better when compared to the Section \ref{subse:obs_test_plan_all_15min}. Which means by adding more resources to the \acrshort{wdias}, it can handle more workload on the system.

@@

\paragraph{Resource Utilization}
Since \acrshort{wdias} using the \acrshort{k8s} as the container orchestration system, it allows to scale up and cool down the system as required based on the workload. This demonstrate on the test plan of Section \ref{subse:obs_test_plan_all_auto_15min}, and the system get scale up to the maximum at the peak time. Then cool down to single pod after finishing the test cases.
Given above \acrshort{wdias} can run from 1 CPU node to nodes with 100 CPUs. As described in the Section \ref{se:microservice}, it uses the many of the concept of modern microservice architecture to create stateless, failover, redundant microservice to achieve such capabilities.

@@

\paragraph{Grid data performance}
As mentioned in the Section \ref{se:conclusion}, the adapter-grid is using a Python wrapper for netCDF FORTRAN implementation with parallel IO enabled. This has some performance issues as well as memory leak issues. Since each microservice in the \acrshort{wdias} independent of technology that can use to implement the service, it will increase the performance if the adapter-grid directly ported to netCDF with a low level language such as C or FORTRAN. They are some future work that can focus on improving the performance of grid data.

@@

\paragraph{Further improve hierarchical database performance}
As further described in Section \ref{se:conclusion}, it is possible to increase the performance of these bottlenecks much higher such as using \acrshort{influxdb} Commercial cluster support for high availability or horizontal scaling of \acrshort{influxdb}. With \acrshort{influxdb} cluster, it is possible to run multiple pods of adapter-scalar and adapter-vector for support more server hits per second.
Other than that, the \acrshort{wdias} performance can improve via partitioning the timeseries key space into multiple \acrshort{influxdb} instances. The adapter-scalar or adapter-vector can improve to plug multiple instance of \acrshort{influxdb} instances by changing the configurations. As an example, based on the key attribute Section \ref{subse:timeseries_key_attributes} Timeseries Type, the adapter-scalar can connect to four instance of \acrshort{influxdb} instances such as  External Historical, External Forecast, Simulated Historical, and Simulated Forecast etc.

@@

\acrshort{wdias} performance test is perform using the \acrshort{jmeter} tool's distributed testing capabilities which separately testing each modules. Then the test plans are performed with increasing the request size, and monitored the performance metrics. The system is setup on the \acrfull{eks} as per the configurations of Section \ref{subse:test_sys_config}.
During the performance test plans, the system were able to provide constant throughput by keeping the latency constant while increasing the workload. Which exhibit the scalability of the system.
With the \acrshort{k8s} auto scaling, the \acrshort{wdias} were able to elastically adjust the number of pods according to the workload with the given configurations.

### 2020-02-13 method/sec_0_introduction.tex
Fixed: “Section”
- Add “Section”
- “section” -> “Section”

This chapter includes the design decision taken while implementing the \acrfull{wdias}, and how is the system got adapted from the systems analyzed in Chapter \ref{ch:literature}. %, then how is it trying to propose a better system with overcoming the issues.
In Section \ref{se:high_level_design} a brief discussion on how the weather forecasting is happening and why it need to interact with multiple data formats is presented. Then following subsections define few termelogy which are using in the \acrshort{wdias}, and scope of the thesis.
Section \ref{se:architectural_decisions} that we evolve over while designing and implementing the \acrshort{wdias}.
The section \ref{se:microservice} gives better understanding of the microservice architectural concepts follows while implementing the \acrshort{wdias}.
Then the reason behind developing Heirarchital Database and technologies use for that discussed in the section \ref{se:db_struct}.
Throw out the section \ref{se:data_preprocess} discussed about how the \acrshort{wdias} enable for data preprocessing and adding capabilities via concept of Extensions.
Finally, in Section \ref{se:query} includes details on how to perform timeseries search and geo based queries.

>>>>

This chapter includes the design decision taken while implementing the \acrfull{wdias}, and how is the system got adapted from the systems analyzed in Chapter \ref{ch:literature}. %, then how is it trying to propose a better system with overcoming the issues.
In Section \ref{se:high_level_design} a brief discussion on how the weather forecasting is happening and why it need to interact with multiple data formats is presented. Then following subsections define few termelogy which are using in the \acrshort{wdias}, and scope of the thesis.
Section \ref{se:architectural_decisions} that we evolve over while designing and implementing the \acrshort{wdias}.
The Section \ref{se:microservice} gives better understanding of the microservice architectural concepts follows while implementing the \acrshort{wdias}.
Then the reason behind developing Heirarchital Database and technologies use for that discussed in the Section \ref{se:db_struct}.
Throw out the Section \ref{se:data_preprocess} discussed about how the \acrshort{wdias} enable for data preprocessing and adding capabilities via concept of Extensions.
Finally, in Section \ref{se:query} includes details on how to perform timeseries search and geo based queries.

### 2020-02-13 method/sec_3-microservice.tex
Problem statement
Fixed: “Section”
- Add “Section”
- “section” -> “Section”

When building communication endpoints, \hl{many architecture approach with putting significant smart into the communication mechanism.} One good example is \acrshort{esb} what we discussed in section \ref{se:architectural_decisions}. But microservice follows alternative approach: \emph{Smart endpoints and dumb pipes} \cite{LewisMicroservicesPipes}.
Applications built from microservices aim to be as decoupled and as cohesive as possible. They own their own domain logic and act more as filters in the classical Unix sense. After receiving a request, applying logic as appropriate and producing a response. And it uses simple RESTish protocols rather than complex protocols.
\dbc{RESTish or RESTful?}

@@

\\paragraph{Z-axis Scaling}-- When using x-axis scaling each server runs an identical copy of the code (similar to X-axis scaling). The big difference is that each server is responsible for only a subset of the data. 
Z-axis splits are commonly used to scale databases. Data is partitioned (a.k.a. sharded) across a set of servers based on an attribute of each record.

Even \acrshort{wdias} is design based on the Y-axis scaling, it's possible to use the Z-axis scaling to scalability of the system further. This will be more discuss in the section \ref{se:discussion}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{\acrshort{wdias} Microservices}
\label{sebse:wdias_microservices}
As seen in Figure of \ref{fi:wdias_micro_on_demand} and \ref{fi:wdias_micro_async} each circle represents a microservice, and those are implemented as containerized applications.
\begin{figure}[htp]
    \centering
    \includegraphics[width=1\textwidth]{method/microservice/microservice_architecture-handle_on_demand-v3.jpg}
    \caption{\acrshort{wdias} architecture \hl{for server requests on demand}}
    \label{fi:wdias_micro_on_demand}
\end{figure}
Left side of Figure \ref{fi:wdias_micro_on_demand} shows the import modules of the \acrshort{wdias}, and right side shows the export modules. As it explained section \ref{subse:dumb_pipes}, each import microservice only do specific task of converting and forwarding the request to the correct data adapter module.
For each data type, there is a adapter microservice is running which is optimized to storing such type of data. And the metadata data of the timeseries store using \acrshort{rdbms} which gives more performance over retrieving metadata data. The metadata is cached with In-Memory database to fast access as mentioned in section \ref{subse:redis}.
The system generate a unique identifier for each timeseries, and throw out the \acrshort{wdias}, other microservice use it to handle data for fast access.

\begin{figure}[htp]
    \centering
    \includegraphics[width=1\textwidth]{method/microservice/microservice_architecture-handle_on_async-v3.jpg}
    \caption{\acrshort{wdias} architecture for handling requests asynchronously.}
    \label{fi:wdias_micro_async}
\end{figure}
Export module microservice follows the same concepts and provide the capability to export the data into required formats of the weather models.
Each adapter follows the concept of database per service as mentioned in the section \ref{subse:database_per_service}. This gives the freedom for \acrshort{wdias} to scale better with \acrshort{k8s}.

As shown in Figure \ref{fi:wdias_micro_on_demand}, when a smaller size request come to the system, it handle on demand and response back. However, as shown in Figure \ref{fi:wdias_micro_async}, when a request with larger size come to the system, it store the data for asynchronously process the data and response with a unique id which can use to verify whether data processed successfully or not. Here is uses the microservice pattern of \ref{subse:sagas} while processing the Grid data. First it store the data and respond back to the user. Then publish an event, and another service listen to those events and process the data and update the system status.

\begin{figure}[htp]
    \centering
    \includegraphics[width=1\textwidth]{method/microservice/separation_microservices-v3.jpg}
    \caption{Separation of \acrshort{wdias} microservices.}
    \label{fi:wdias_micro_separation}
\end{figure}
The figure \ref{fi:wdias_micro_on_demand} show the clear separation of microservices into the modules of the \acrshort{wdias}. As it shown, each adapter has isolated database, and database is hosted separately for the high performance.
Apart from that, as we further discuss in section \ref{se:data_preprocess}, the extension modules are running separately such as Interpolation, Transformation and Validation etc.
The Extension Adapter allow users to register new triggers for the extensions. And extension scheduler triggers the events based on time and extension handler triggers event based on data change.

@@

\emph{Extensions} endpoints for configure extensions. These details describes in the section \ref{se:data_preprocess}.

>>>>

When building communication endpoints, \hl{many architecture approach with putting significant smart into the communication mechanism.} One good example is \acrshort{esb} what we discussed in Section \ref{se:architectural_decisions}. But microservice follows alternative approach: \emph{Smart endpoints and dumb pipes} \cite{LewisMicroservicesPipes}.
Applications built from microservices aim to be as decoupled and as cohesive as possible. They own their own domain logic and act more as filters in the classical Unix sense. After receiving a request, applying logic as appropriate and producing a response. And it uses simple RESTish protocols rather than complex protocols.
\dbc{RESTish or RESTful?}

@@

\paragraph{Z-axis Scaling}-- When using x-axis scaling each server runs an identical copy of the code (similar to X-axis scaling). The big difference is that each server is responsible for only a subset of the data. 
Z-axis splits are commonly used to scale databases. Data is partitioned (a.k.a. sharded) across a set of servers based on an attribute of each record.

Even \acrshort{wdias} is design based on the Y-axis scaling, it's possible to use the Z-axis scaling to scalability of the system further. This will be more discuss in the Section \ref{se:discussion}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{\acrshort{wdias} Microservices}
\label{sebse:wdias_microservices}
As seen in Figure of \ref{fi:wdias_micro_on_demand} and \ref{fi:wdias_micro_async} each circle represents a microservice, and those are implemented as containerized applications.
\begin{figure}[htp]
    \centering
    \includegraphics[width=1\textwidth]{method/microservice/microservice_architecture-handle_on_demand-v3.jpg}
    \caption{\acrshort{wdias} architecture \hl{for server requests on demand}}
    \label{fi:wdias_micro_on_demand}
\end{figure}
Left side of Figure \ref{fi:wdias_micro_on_demand} shows the import modules of the \acrshort{wdias}, and right side shows the export modules. As it explained section Section \ref{subse:dumb_pipes}, each import microservice only do specific task of converting and forwarding the request to the correct data adapter module.
For each data type, there is a adapter microservice is running which is optimized to storing such type of data. And the metadata data of the timeseries store using \acrshort{rdbms} which gives more performance over retrieving metadata data. The metadata is cached with In-Memory database to fast access as mentioned in Section \ref{subse:redis}.
The system generate a unique identifier for each timeseries, and throw out the \acrshort{wdias}, other microservice use it to handle data for fast access.

\begin{figure}[htp]
    \centering
    \includegraphics[width=1\textwidth]{method/microservice/microservice_architecture-handle_on_async-v3.jpg}
    \caption{\acrshort{wdias} architecture for handling requests asynchronously.}
    \label{fi:wdias_micro_async}
\end{figure}
Export module microservice follows the same concepts and provide the capability to export the data into required formats of the weather models.
Each adapter follows the concept of database per service as mentioned in the section Section \ref{subse:database_per_service}. This gives the freedom for \acrshort{wdias} to scale better with \acrshort{k8s}.

As shown in Figure \ref{fi:wdias_micro_on_demand}, when a smaller size request come to the system, it handle on demand and response back. However, as shown in Figure \ref{fi:wdias_micro_async}, when a request with larger size come to the system, it store the data for asynchronously process the data and response with a unique id which can use to verify whether data processed successfully or not. Here is uses the microservice pattern of Section \ref{subse:sagas} while processing the Grid data. First it store the data and respond back to the user. Then publish an event, and another service listen to those events and process the data and update the system status.

\begin{figure}[htp]
    \centering
    \includegraphics[width=1\textwidth]{method/microservice/separation_microservices-v3.jpg}
    \caption{Separation of \acrshort{wdias} microservices.}
    \label{fi:wdias_micro_separation}
\end{figure}
The figure \ref{fi:wdias_micro_on_demand} show the clear separation of microservices into the modules of the \acrshort{wdias}. As it shown, each adapter has isolated database, and database is hosted separately for the high performance.
Apart from that, as we further discuss in Section \ref{se:data_preprocess}, the extension modules are running separately such as Interpolation, Transformation and Validation etc.
The Extension Adapter allow users to register new triggers for the extensions. And extension scheduler triggers the events based on time and extension handler triggers event based on data change.

@@

\emph{Extensions} endpoints for configure extensions. These details describes in the Section \ref{se:data_preprocess}.

### 2020-02-13 method/sec_4-db_struct.tex
Fixed: “Section”
- Add “Section”
- “section” -> “Section”

%There are lots of \acrshort{rdbms} available and for 
\acrshort{wdias} is using SQL as the \acrfull{rdbms}. 
%SQL database has fewer version of open source and it is also possible to gain better performance with commercial versions. 
Since WDIAS scope is to using open source tools, it is using \acrshort{mysql} as persistent database for storing timeseries metadata described above.
One instance of \acrshort{mysql} is using only by adapter-metadata service.
Other than that, another instance of \acrshort{mysql} is using for adapter-extension which will be describe in more detail \ref{se:data_preprocess}.
\acrshort{mysql} is used only for these services, those will only keep the consistency of the schema for timeseries metadata and extension metadata.
\ref{subse:redis} instance is using for caching the data from \acrshort{mysql}, since the \acrshort{mysql} database instances, itself not going to get much load.
Other than MySQL, there are many open source databases can be used to replace the same functionality.
\dbc{First start with a brief discussion on why a RDBMS is needed}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Timeseries Database}
\label{subse:influxdb}
Among several timeseries open source databases, \acrshort{influxdb} \cite{influxdbInfluxDBDocumentation} \hl{has higher number of usage and support. Database is written in Golang programming language, and} has higher performance, and has following supports;
\begin{itemize}
  \item Open timeseries DB with MIT license
  \item Support SQL-Like query language
  \item Clustering available with a commercial version
\end{itemize}
Other than \acrshort{influxdb}, another database is Elastic Search which is mainly using for indexing for searching.
With changing the configurations of the \acrshort{influxdb}, it is possible to adapt as required. As mention in \cite{influxdbInfluxDBDocumentation}, 
\acrshort{influxdb} can setup on a computer which will give the required performance. Going further, users can use commercial version of \acrshort{influxdb} in order to gain more performance.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{In-Memory Database}
\label{subse:redis}
\acrshort{wdias} is using \acrshort{redis} \cite{redisRedisDocumentation} as the In-Memory database, since it's widely using tool with good support, and it support few other features such as Publisher Subscriber capabilities.
\acrshort{redis} is an open source (BSD licensed), used as a database, cache. Clustering is available for scalability.
\acrshort{redis} uses as in-memory caching for fast access of repreative access data in adapter-metadata and adapter-extension.
Other than that, adapter-status uses \acrshort{redis} as key value pair store for getting the status for async handling requests such as storing Grid data.
In adapter-extension uses Redis's Publisher Subscriber capabilities in order to create a cron job in extension-scheduler when new extension create on \ref{se:data_preprocess}

>>>>

%There are lots of \acrshort{rdbms} available and for 
\acrshort{wdias} is using SQL as the \acrfull{rdbms}. 
%SQL database has fewer version of open source and it is also possible to gain better performance with commercial versions. 
Since WDIAS scope is to using open source tools, it is using \acrshort{mysql} as persistent database for storing timeseries metadata described above.
One instance of \acrshort{mysql} is using only by adapter-metadata service.
Other than that, another instance of \acrshort{mysql} is using for adapter-extension which will be describe in more detail Section \ref{se:data_preprocess}.
\acrshort{mysql} is used only for these services, those will only keep the consistency of the schema for timeseries metadata and extension metadata.
As mentioned in Section \ref{subse:redis}, it uses \acrshort{redis} instance is using for caching the data from \acrshort{mysql}, since the \acrshort{mysql} database instances, itself not going to get much load.
Other than MySQL, there are many open source databases can be used to replace the same functionality.
\dbc{First start with a brief discussion on why a RDBMS is needed}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Timeseries Database}
\label{subse:influxdb}
Among several timeseries open source databases, \acrshort{influxdb} \cite{influxdbInfluxDBDocumentation} \hl{has higher number of usage and support. Database is written in Golang programming language, and} has higher performance, and has following supports;
\begin{itemize}
  \item Open timeseries DB with MIT license
  \item Support SQL-Like query language
  \item Clustering available with a commercial version
\end{itemize}
Other than \acrshort{influxdb}, another database is Elastic Search which is mainly using for indexing for searching.
With changing the configurations of the \acrshort{influxdb}, it is possible to adapt as required. As mention in \cite{influxdbInfluxDBDocumentation}, 
\acrshort{influxdb} can setup on a computer which will give the required performance. Going further, users can use commercial version of \acrshort{influxdb} in order to gain more performance.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{In-Memory Database}
\label{subse:redis}
\acrshort{wdias} is using \acrshort{redis} \cite{redisRedisDocumentation} as the In-Memory database, since it's widely using tool with good support, and it support few other features such as Publisher Subscriber capabilities.
\acrshort{redis} is an open source (BSD licensed), used as a database, cache. Clustering is available for scalability.
\acrshort{redis} uses as in-memory caching for fast access of repreative access data in adapter-metadata and adapter-extension.
Other than that, adapter-status uses \acrshort{redis} as key value pair store for getting the status for async handling requests such as storing Grid data.
In adapter-extension uses Redis's Publisher Subscriber capabilities in order to create a cron job in extension-scheduler when new extension create on Section \ref{se:data_preprocess}

### 2020-02-13 results/sec_0-introduction.tex
Reviewed again after PGS reject
Fixed: “Section”
- Add “Section”
- “section” -> “Section”

This chapter includes performance study of the \acrshort{wdias}. In the first section \ref{se:test_plan} describes the planned method of testing the system.
In the next section \ref{se:workload} describes the logic behind creating the workload to do the performance testing planned in \ref{se:test_plan}.
Following section \ref{se:observations} includes the results observed while performance study. And summarised the observations in the next section \ref{se:discussion}.

>>>>

This chapter includes performance study of the \acrshort{wdias}. In Section \ref{se:test_plan} describes the planned method of testing the system.
In the next Section \ref{se:workload} describes the logic behind creating the workload to do the performance testing planned in Section \ref{se:test_plan}.
Following Section \ref{se:observations} includes the results observed while performance study. And summarised the observations in the next Section \ref{se:discussion}.

### 2020-02-13 results/sec_2-workload.tex
Problem statement
Fixed: “Section”
- Add “Section”
- “section” -> “Section”

As explained in Section \ref{ch:method}, timeseries has six primary attributes. In order to create a timeseries for performance testing, it needs data for each key attribute.
While generating the timeseries for performance testing, it selected locations all over the world as a generic case to include all the locations without binding to a specific area.

@@

For grid data, it uses static 100 grid locations which based on how is \acrshort{api} exposed. Since grid locations have different metadata structure as described in \ref{se:db_struct}, those data handle separately. But the locationId of grid and scalar data types have the same effect when define a timeseries.

In the \acrshort{jmeter} Best Practices, \say{If your test needs large amounts of data - particularly if it needs to be \emph{randomised} create the test data in a file that can be read with CSV Data set. This avoids wasting resources at run-time. jmeter best practices lean\_mean}. Rather providing the randomness in run time, the timeseries stored with the random order which satisfy the percentage of 70\% Scalar, 20\% Vector and 10\% Grid as mentioned in \ref{se:test_plan}.
Before running the test cases, it generate the metadata for timeseries and write into a CSV file which is shared among the threads in the \acrshort{jmeter}. This occurs in the setup phase of the test cases. The metadata CSV file arrange in a way that within each 10 lines, 7 lines are Scalar timeseries, 2 lines are Vector timeseries, and 1 line is a Grid timeseries.

@@

The test plans mentioned in \ref{se:test_plan} are implemented via the \acrshort{jmeter}. The following list shows the all the test cases used for the performance testing:

@@

It allows to run particular test plan which are described in \ref{se:test_plan}. Also possible to run the all the test plans in order with given \emph{REQ\_SIZE} or for all the \emph{REQ\_SIZE}.

\subsubsection{JMeter performance tuning}
\begin{itemize}
    \item Use CSV files rather thanrandom number generation
    \item Use JSR223 scripts with Groovy for data processing for test cases
    \item Using Throughput Shaping Timer to get more accurate \acrshort{rps}
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{\hl{System Configuration}}
\label{subse:test_sys_config}
As described in the \ref{se:microservice}, the \acrshort{wdias} is mainly focus on microservice architecture and implemented on top of kubernetes. \acrfull{k8s} is an open-source system for automating deployment, scaling, and management of containerized applications. For the performance study uses \acrfull{eks}. There are many \acrshort{k8s} solutions available such as GCP, Azure, and Digital Ocean on the cloud.

A detailed description of setting up the \acrshort{eks} available as \cite{KarunarathneWdias/Amazon_EKS.md:EKS} within the main repository of the \acrshort{wdias}.
\acrshort{k8s} is a planet scaling tool \cite{LinuxFoundationProduction-GradeKubernetes}, and users can tweak the configuration to run the \acrshort{wdias} as per the required level of load on the system. During the performance test of the \acrshort{wdias}, it uses maximum of 300 \acrshort{rps} with providing to the system with increasing load, and monitor the auto scalability of the system with measuring other performance parameters mentioned in Table \ref{se:test_plan}.

>>>>

As explained in Chapter \ref{ch:method}, timeseries has six primary attributes. In order to create a timeseries for performance testing, it needs data for each key attribute.
While generating the timeseries for performance testing, it selected locations all over the world as a generic case to include all the locations without binding to a specific area.

@@

For grid data, it uses static 100 grid locations which based on how is \acrshort{api} exposed. Since grid locations have different metadata structure as described in Section \ref{se:db_struct}, those data handle separately. But the locationId of grid and scalar data types have the same effect when define a timeseries.

In the \acrshort{jmeter} Best Practices, \say{If your test needs large amounts of data - particularly if it needs to be \emph{randomised} create the test data in a file that can be read with CSV Data set. This avoids wasting resources at run-time. jmeter best practices lean\_mean}. Rather providing the randomness in run time, the timeseries stored with the random order which satisfy the percentage of 70\% Scalar, 20\% Vector and 10\% Grid as mentioned in Section \ref{se:test_plan}.
Before running the test cases, it generate the metadata for timeseries and write into a CSV file which is shared among the threads in the \acrshort{jmeter}. This occurs in the setup phase of the test cases. The metadata CSV file arrange in a way that within each 10 lines, 7 lines are Scalar timeseries, 2 lines are Vector timeseries, and 1 line is a Grid timeseries.

@@

The test plans mentioned in Section \ref{se:test_plan} are implemented via the \acrshort{jmeter}. The following list shows the all the test cases used for the performance testing:

@@

It allows to run particular test plan which are described in Section \ref{se:test_plan}. Also possible to run the all the test plans in order with given \emph{REQ\_SIZE} or for all the \emph{REQ\_SIZE}.

\subsubsection{JMeter performance tuning}
\begin{itemize}
    \item Use CSV files rather than random number generation
    \item Use JSR223 scripts with Groovy for data processing for test cases
    \item Using Throughput Shaping Timer to get more accurate \acrshort{rps}
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{\hl{System Configuration}}
\label{subse:test_sys_config}
As described in the Section \ref{se:microservice}, the \acrshort{wdias} is mainly focus on microservice architecture and implemented on top of kubernetes. \acrfull{k8s} is an open-source system for automating deployment, scaling, and management of containerized applications. For the performance study uses \acrfull{eks}. There are many \acrshort{k8s} solutions available such as GCP, Azure, and Digital Ocean on the cloud.

A detailed description of setting up the \acrshort{eks} available as \cite{KarunarathneWdias/Amazon_EKS.md:EKS} within the main repository of the \acrshort{wdias}.
\acrshort{k8s} is a planet scaling tool \cite{LinuxFoundationProduction-GradeKubernetes}, and users can tweak the configuration to run the \acrshort{wdias} as per the required level of load on the system. During the performance test of the \acrshort{wdias}, it uses maximum of 300 \acrshort{rps} with providing to the system with increasing load, and monitor the auto scalability of the system with measuring other performance parameters mentioned in Table \ref{tab:aws_eks_nodes}.
